\section{Background on Application }

%describe the DAS application (1 paragraph) and its requirements (1 paragraph per each of consistency, scalability, fault - tolerance, and performance ).

The Dragon Arena System (DAS) is an online warfare game of WantGame BV between human players and computer controlled dragons.
The game consists of a battlefield of 25x25 squares on which players and dragons reside.
The goal of the game for the players is to kill all the dragons and survive (vice versa for the dragons).
WantGame want the game to be able to support many concurrent users and has therefore decided to invest in, and design a distributed game engine which needs to be consistent, scalable and fault-tolerant. 

As stated, the game needs to support multiple concurrent users playing on the same battlefield. 
This means that the system must be able to scale up in order to handle all these users and the requests they make to the servers. 
In order to achieve this, it is important to have multiple server nodes to handle requests of all these users. 
(This will be explained in more detail in the next section).

%%%% MAYBE THIS PART IS SOLUTIONS SO MOVE TO DESIGN?
Multiple nodes means that different players may be performing actions which has an impact on a second player's actions.
In order to detect this, the system needs to be able to detect whether another players action is still valid. 
A possible solution for this problem may be to use causal ordering for player actions. %%% OR JUST THIS SENTENCE

Last but not least, players must be able to continue their game even if some server crashes. 
A possible approach to address this issue may lie in concurrent copies. %%%% AND THIS
This ensures that there is at least more than one copy of a running instance of the game to make sure that clients can silently reconnect to another server without disrupting the users game experience. 
