\documentclass{article}
\usepackage{a4wide}
\usepackage{graphicx}
\usepackage{hyperref}

%% if your are not using LaTeX2e use instead
%% \documentstyle[bnaic]{article}

%% begin document with title, author and affiliations

\title{Distributed Computing Systems IN4391\\ The Dragons Arena System %: Distributed Simulation of Virtual Worlds
}
\author{Patrick Brand (p.brand@student.tudelft.nl) \and
    Raies Saboerali (r.a.a.saboerali@student.tudelft.nl)
	%\thanks	T.A: Ir. Mihai Capota, Course Manager: Dr.ir. Alexandru IOSUP
}
\date{\today}

%support cast needs to be filled in here.


\pagestyle{empty}

\begin{document}
\maketitle
\thispagestyle{empty}
\begin{center}
Lab Assistant: Ir. Mihai Capot$\breve{a}$ \\
Course Instructor: Dr.ir. Alexandru Iosup
\end{center}

\begin{abstract}
%a description of the problem, system description, analysis overview, and one main result. Size: one paragraph with at most 150 words.

This report discusses the process of implementing a distributed version of the Dragon Arena System (DAS) in order to be scalable and to support multiple concurrent users playing the game.
The DAS is a game in which there are players and dragons which can attack each other. 
The goal for the players is to survive by killing the dragons and vice versa for the dragons.

The game architecture consists of two main layers; the helper server layer and the main server layer.
The helper servers perform computations and the servers in the main layer keep track of the battlefield and eventual copies of the battlefield.
The communication between the helper servers and the clients is done via Java's Remote Method Invocation.

The new DAS will be scalable up to a hundred players and allow players to play uninterrupted even when faults occur.


\end{abstract}


\section{Introduction}

%(recommended size, including points 1 and 2: 1 page): describe the problem, the existing systems and/or tools about which you know (related work), the system you are about to implement, and the structure of the remainder of the article. Use one short paragraph for each.

% The problem
The Dragon Arena System (DAS) is a (non-distributed) online warfare game of WantGame BV.
Now, WantGame BV wishes to implement a new, distributed, version of the DAS in order to be able to support many concurrent users.
However, designing and implementing a distributed system which has to support massive amounts of concurrent users is rather complex as it introduces many unknowns with regard to properties such as performance, scalability, consistency and fault-tolerance.

% Existing systems and/or tools which you know
A previous non-distributed version of a DAS, which was implemented by a previous consultant of WantGame BV, has been studied carefully before the design of the new distributed DAS.
The new Dragon Arena System game is implemented in Java and uses Remote Method Invocation (RMI) in order to support remote calls to other clients and servers.

% The system you are about to implement
The newly designed and implemented DAS aims to be scalable in the sense that it needs to run a service of online warfare between computer- controlled dragons and hundreds of clients, who are represented by virtual knights. 
A distributed implementation of the game provides a better performance-cost ratio as the implemented system uses resources more efficient than the old implementation of the game.
Such a system also allows the workload to be distributed over multiple server nodes which leads to a better performance than just a client-server approach.

% Structure of the remainder of the article
This report starts with addressing the application itself and its background in section two.
Afterwards, the design and architecture of the proposed system which is implemented is discussed in the third section.
The various high level components of the game and how they communicate are explained there as well.
In the fourth section the results of various performed tests are presented. 
Furthermore, a discussion about the findings of our work can be found in the fifth section and finally it ends with a conclusion in section six. The appendix hosts a list with spent hours as well as a personal evaluation of this project.

\newpage

\input{1-background-on-application}

\input{2-system-design}

\input{3-experimental-results}

\input{4-discussion}

\input{5-conclusion}  

\include{appendix}

\nocite{*}
\bibliographystyle{plain}
\bibliography{mybibfile}

\end{document}








